---
title: "From spirit to letter"
author: "Ivar Rodríguez Hannikainen"
output:
  html_document:
    df_print: paged
    
---

### Loading libraries

We load the required libraries.

```{r message=FALSE, libraries}
library(tidyverse)
library(readr)
library(emmeans)
library(readxl)
library(lmerTest)
library(optimx)
```

### Import data

```{r message = FALSE, import}
filename1 = "Data/child_data.csv"
# Deleting 1st column
headers1 = read_csv(filename1, col_names = FALSE, n_max = 1)
# Raw data (deleting 3 rows)
dev_child = read_csv(filename1, skip = 3, col_names = FALSE)
# Naming raw date (with "headers")
colnames(dev_child) = headers1

filename2 = "Data/adult_data.csv"
# Deleting 1st column
headers2 = read_csv(filename2, col_names = FALSE, n_max = 1)
# Raw data (deleting 3 rows)
dev_adult = read_csv(filename2, skip = 3, col_names = FALSE)
# Naming raw date (with "headers")
colnames(dev_adult) = headers2

# manual colname update
colnames(dev_child)[22:45] = c('c1', 'n1', 'u1', 'o1',
                          'c2', 'n2', 'o2', 'u2',
                          'n3', 'c3', 'o3', 'u3',
                          'c4', 'n4', 'u4', 'o4',
                          'c5', 'n5', 'o5', 'u5',
                          'n6', 'c6', 'o6', 'u6')

colnames(dev_adult)[19:42] = c('c1', 'n1', 'u1', 'o1',
                          'c2', 'n2', 'o2', 'u2',
                          'n3', 'c3', 'o3', 'u3',
                          'c4', 'n4', 'u4', 'o4',
                          'c5', 'n5', 'o5', 'u5',
                          'n6', 'c6', 'o6', 'u6')
```

We have 

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file). 

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

